Towards Compiler-Agnostic Performance in Finite-Difference Codes

### 2015-08-07 shallow_perf.tex
Change Manish affiliation to Hartree and acknowledge use of Hartree P8 system

\begin{document}

@@

\author[A]{\fnms{A. R.} \snm{Porter}%
\thanks{Corresponding Author: Andrew Porter, STFC Daresbury Laboratory, Warrington, WA4 4AD, UK; E-mail:
andrew.porter@stfc.ac.uk.}},
\author[A]{\fnms{R. W.} \snm{Ford}},
\author[A]{\fnms{M.} \snm{Ashworth}},
\author[A]{\fnms{G. D.} \snm{Riley}}
and
\author[B]{\fnms{M.} \snm{Modani}}
\runningauthor{A.~R.~Porter et al.}
\address[A]{STFC Daresbury Laboratory, Warrington, WA4 4AD, UK}
\address[B]{IBM India}

@@

This work made use of the ARCHER UK National Supercomputing Service
(\url{http://www.archer.ac.uk}). This work was funded by NERC project {\bf xxx}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

@@

\author[A]{\fnms{A. R.} \snm{Porter}%
\thanks{Corresponding Author: Andrew Porter, STFC Daresbury Laboratory, Warrington, WA4 4AD, UK; E-mail:
andrew.porter@stfc.ac.uk.}},
\author[A]{\fnms{R. W.} \snm{Ford}},
\author[A]{\fnms{M.} \snm{Ashworth}},
\author[B]{\fnms{G. D.} \snm{Riley}}
and
\author[C]{\fnms{M.} \snm{Modani}}
\runningauthor{A.~R.~Porter et al.}
\address[A]{STFC Daresbury Laboratory, Warrington, WA4 4AD, UK}
\address[B]{The University of Manchester, UK}
\address[C]{STFC Hartree Centre}

@@

This work made use of the ARCHER UK National Supercomputing Service
(\url{http://www.archer.ac.uk}). We acknowledge use of the Hartree
Centre IBM Power 8 system in this work. The STFC Hartree Centre is a
research collaboratory in association with IBM providing High
Performance Computing platforms funded by the UK's investment in
e-Infrastructure. The Centre aims to develop and demonstrate next
generation software, optimised to take advantage of the move towards
exa-scale computing. This work was funded by NERC project {\bf xxx}
